Parallel Adaptive Importance Sampling

### 2015-08-26 PAIS.tex
Spellcheck and cover letter
Added a cover letter and did a spell check.

The graphs in the previous section clearly show that the PAIS-pCNL algorithm converges faster than the pCNL algorithm when both are parallelised with the same number of threads. We can calculate the number of iterations required to achieve a particular tolerance level in our solution for each algorithm and compare these to calculate a percentage saving. In Figure~\ref{fig:calc_saving} we demonstrate our calculation of the savings. The constants $c_1$ and $c_2$ are found by regressing through the data with a fixed exponent of $-1/2$ excluding the intial data points where the graph has not finished burning in.

>>>>

The graphs in the previous section clearly show that the PAIS-pCNL algorithm converges faster than the pCNL algorithm when both are parallelised with the same number of threads. We can calculate the number of iterations required to achieve a particular tolerance level in our solution for each algorithm and compare these to calculate a percentage saving. In Figure~\ref{fig:calc_saving} we demonstrate our calculation of the savings. The constants $c_1$ and $c_2$ are found by regressing through the data with a fixed exponent of $-1/2$ excluding the initial data points where the graph has not finished burning in.
